A Process for Emulating Comparative Oncology Trials with Real-world Evidence Studies (ENCORE): Process Development and Methodological Considerations for Oncology Real-World Data

### 2025-05-28 manuscript/manuscript.tex
Manuscript updated

\emph{Manuscript last updated: 2025-05-28 16:51:13.630823}

@@

A list of tentative, shortlisted primary candidates is presented in
Table~\ref{tbl-rcts}. The corresponding selection process is illustrated
in the CONSORT diagrams (\textbf{Supplementary Figures 1-4}) and runner
up candidate trials are listed in \textbf{Supplementary Table 1}.
Naturally, the majority of shortliested trials cover advanced (locally
advanced, inoperable, recurrent/progressive disease) or metastatic
cancer populations because a large proportion of drug development
efforts have recently focused on these settings. A key objective that we
aim to explore with the selected trials is to achieve a better
understanding how different disease settings (early, late), line
settings ({[}neo{]}adjuvant, first line, advanced lines of therapy),
therapy protocols (monotherapy, combination therapy) and clinical
characteristics (all-comer versus complex genetic or immunological
signatures) can be emulated using RWD. If more thorough feasibility
assessments after applying all relevant eligibility criteria suggest
that the threat of bias from mis-measurement of key study parameters or
residual confounding remains high, or that the study size is not
sufficient, then runner-up candidate trials will be considered instead.

>>>>

\emph{Manuscript last updated: 2025-05-28 17:11:23.084986}

@@

A list of tentative, shortlisted primary candidates is presented in
Table~\ref{tbl-rcts}. The corresponding selection process is illustrated
in the CONSORT diagrams (\textbf{Supplementary Figures 1-4}) and runner
up candidate trials are listed in \textbf{Supplementary Table 1}.
Naturally, the majority of shortlisted trials cover advanced (locally
advanced, inoperable, recurrent/progressive disease) or metastatic
cancer populations because a large proportion of drug development
efforts have recently focused on these settings. A key objective that we
aim to explore with the selected trials is to achieve a better
understanding how different disease settings (early, late), line
settings ({[}neo{]}adjuvant, first line, advanced lines of therapy),
therapy protocols (monotherapy, combination therapy) and clinical
characteristics (all-comer versus complex genetic or immunological
signatures) can be emulated using RWD. If more thorough feasibility
assessments after applying all relevant eligibility criteria suggest
that the threat of bias from mis-measurement of key study parameters or
residual confounding remains high, or that the study size is not
sufficient, then runner-up candidate trials will be considered instead.
